Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-10-15 paper/sections/discussion.tex
[ paper ] introduction added to emulate rules section.
[ paper ] first description version for canonicalize.

@@

\textit{Clausification.} The \clausify rule transforms a
propositional formula in clausal normal form, a conjunction
of clauses. Where a \emph{clause} is the disjunction of zero or more
literals and a \emph{literal} is an atom (positive literal) or a
negation of an atom (negative literal). Be aware this kind of conversion between one formula to its clausal normal form is not unique, and \Metis has a customized approach to perform that transformation. We refer the reader to see Section~\ref{sssec:clausification} for the formalization of \clausify rule.

@@

% ...................................................................
\vskip 2mm

\textit{Resolution.} The \resolve rule incorporates the resolution theorem showed in Fig.~\ref{fig:metis-inferences} for the \TSTP derivations.
This rule posses three arguments: a positive literal $l$ to apply the resolution theorem, and two derivations, $\mathcal{D}₁$ and $\mathcal{D}₂$.

The positive literal $l$ must occur in
the formula from the first derivation $\mathcal{D}₁$, and the
negative literal must occur in the formula from the second derivation $\mathcal{D}₂$ (see the pattern in the \emph{resolve} rule).
We refer the reader to see Section~\ref{sssec:resolve} for the formalization of the \resolve rule.

\begin{verbatim}
cnf(refute_0_0, plain, p | q,
  inference(canonicalize, [], [normalize_0_0])).
cnf(refute_0_1, plain, ~ p,
  inference(canonicalize, [], [normalize_0_4])).
cnf(refute_0_2, plain, q,
  inference(resolve, [$cnf(p)], [refute_0_0, refute_0_1])).
\end{verbatim}

\textit{Splitting a conjunct.} The \conjunct rule extracts from a
conjunction one of its conjuncts; it is a generalization of the
projection rules for the conjunction connective as the
following \TSTP derivation shows.
We refer the reader to see Theorem~\ref{thm:thm-conjunct}
in Section~\ref{sssec:splitting-a-conjunct} for its formalization.

\begin{verbatim}
fof(normalize_1, plain, p & q & r,
  inference(canonicalize, [], [x])).
fof(normalize_2, plain, q,
  inference(conjunct, [], [normalize_1])).
\end{verbatim}

\textit{Negate.}
Each subgoal proof is a refutation, thereby each proof assumes
the negation of its subgoal. The \negate rule
assumes the negation of a given subgoal. This rules always
appears after applies the \strip inference to the goal.

\begin{verbatim}
fof(subgoal_0, plain, p,
  inference(strip, [], [goal])).
fof(negate_0_0, plain, ~ p,
  inference(negate, [], [subgoal_0])).
\end{verbatim}

\textit{Simplification.}
The \simplify rule is an inference that performs simplification of
definitions and tautologies. This rule
transverses a list of formulas by applying different theorems (e.g.,
\emph{modus pones}, \emph{modus tollens}, or \emph{disjunctive
syllogism}) including the list of theorems used by \canonicalize in
Fig. \ref{fig:conjunctive-disjunctive-simpl} and the resolution
theorem of the \resolve rule.
We refer the reader to see Section~\ref{sssec:simplify}.

>>>>

In the following, we use the \Bool type for booleans defined as usual as
well as $not$ function, $and$ function for the boolean conjunction,
and $if_then_else$ dependent function type.

@@

\textit{Clausification.} The \clausify rule transforms a
propositional formula in its clausal normal form, a conjunction
of clauses. Where a \emph{clause} is the disjunction of zero or more
literals and a \emph{literal} is an atom (positive literal) or a
negation of an atom (negative literal). Be aware this kind of conversion between one formula to its clausal normal form is not unique, and \Metis has a customized approach to perform that transformation. We refer the reader to see Section~\ref{sssec:clausification} for the formalization of \clausify rule.

@@
